Databrary: A digital data library for sharing research video

### 2015-01-14 jcdl-15/paper.tex
Cleanup some cruft and fix syntax errors
Use references and add basic makefile

% This is "sig-alternate.tex" V2.0 May 2012
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

@@

\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{JCDL}{'15 Knoxville, Tennesse USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

\numberofauthors{6}

\author{
\alignauthor
Rick O. Gilmore, Ph.D.\\
	\affaddress{The Pennsylvania State University}\\
	\affaddress{Department of Psychology}\\
	\affadddress{University Park, PA 16802}\\
	\email{rogilmore@psu.edu}

\alignauthor
Lisa A. Steiger\\
	\affaddress{Databrary Project}\\
	\affaddress{New York University}
	\affaddress{196 Mercer Street, Room 807}\\
	\affaddress{New York, NY 10012}\\
	\email{lisa@databrary.org}

\alignauthor
Dylan A. Simon\\
	\affaddress{Databrary Project}\\
	\affaddress{New York University}
	\affaddress{196 Mercer Street, Room 807}\\
	\affaddress{New York, NY 10012}\\
	\email{dylan@databrary.org}

\and

\alignauthor
Drew Gordon\\
	\affaddress{Databrary Project}\\
	\affaddress{New York University}
	\affaddress{196 Mercer Street, Room 807}\\
	\affaddress{New York, NY 10012}\\
	\email{drew@databrary.org}

\alignauthor
David S. Millman\\
	\affaddress{New York University}
	\affaddress{New York, NY 10012}\\
	\email{dsm@nyu.edu}

\alignauthor
Karen E. Adolph, Ph.D.\\
	\affaddress{New York University}
	\affaddress{Department of Psychology}
	\affaddress{New York, NY 10012}\\
	\email{karen.adolph@nyu.edu}

}

@@

**Categories and Subject Descriptors**

@@

REFERENCES
==========

Curry A (2011) Rescue of Old Data Offers Lesson for Particle Physicists.
Science 331:694-695. doi:10.1126/science.331.6018.694

Integrated Earth Data Applications. (2014). http://www.iedadata.org.
Accessed 10 February 2014

Kaye J, Heeney C, Hawkins N, de Vries J, Boddington P (2009) Data
sharing in genomics [mdash] re-shaping scientific practice. Nat Rev
Genet 10 (5):331-335. doi:10.1038/nrg2573

Overpeck JT, Meehl GA, Bony S, Easterling DR (2011) Climate Data
Challenges in the 21st Century. Science 331 (6018):700-702.
doi:10.1126/science.1197869

Lunshof J, Church G, Prainsack B (2014) Raw Personal Data: Providing
Access. Science 343 (6169):373-374. doi:10.1126/science.1249382

Adolph K, Gilmore RO, Freeman C, Sanderson P, Millman D (2012) Toward
Open Behavioral Science. Psychological Inquiry: An International Journal
for the Advancement of Psychological Theory 23 (3):244-247.
doi:10.1080/1047840X.2012.705133

King G (2011) Ensuring the Data-Rich Future of the Social Sciences.
Science 331 (6018):719-721. doi:10.1126/science.1197872.

Association for Psychological Science (2012) Special Section on
Replicability in Psychological Science: A Crisis of Confidence.
Perspectives on Psychological Science 7 (6)

Nosek BA, Bar-Anan Y (2012) Scientific Utopia: I. Opening Scientific
Communication. Psychological Inquiry 23 (3):217-243.
doi:10.1080/1047840X.2012.692215

Nosek BA, Spies JR, Motyl M (2012) Scientific Utopia: II. Restructuring
Incentives and Practices to Promote Truth Over Publishability.
Perspectives on Psychological Science 7 (6):615-631.
doi:10.1177/1745691612459058

MacWhinney B (2001) From CHILDES to TalkBank. In: M. Almgren AB, M.
Ezeizaberrena, I. Idiazabal & B. MacWhinney (ed) Research on Child
Language Acquisition. Cascadilla, Massachusetts, pp 17-34

Cognitive Atlas. (2014). http://www.cognitiveatlas.org. Accessed 10
February 2014

Databrary (2013) Databrary Data Sharing Manifesto.
http://databrary.org/user-guide/policies/data-sharing-manifesto.html.
Accessed 10 February 2014

METS (2014) XSLT-based Metadata Encoding and Transcription Standards
Viewers. http://dlib.nyu.edu/metstools/metsviewer/. Accessed 10 February
2014

HCP (2014) Human Connectome Project.
http://www.humanconnectomeproject.org. Accessed 10 February 2014

PGP (2014) Personal Genome Project. http://www.personalgenomes.org.
Accessed 10 February 2014

>>>>

@@

\begin{document}
\conferenceinfo{JCDL}{'15 Knoxville, Tennesse USA}

@@

\numberofauthors{3}

\author{
\alignauthor
Dylan A. Simon\\
	\affaddr{Databrary Project}\\
	\affaddr{New York University}\\
	\affaddr{196 Mercer Street, Room 807}\\
	\affaddr{New York, NY 10012}\\
	\email{dylan@databrary.org}
\alignauthor
Drew Gordon\\
	\affaddr{Databrary Project}\\
	\affaddr{New York University}
	\affaddr{196 Mercer Street, Room 807}\\
	\affaddr{New York, NY 10012}\\
	\email{drew@databrary.org}
\alignauthor
Rick O. Gilmore, Ph.D.\\
	\affaddr{The Pennsylvania State University}\\
	\affaddr{Department of Psychology}\\
	\affaddr{University Park, PA 16802}\\
	\email{rogilmore@psu.edu}
}

@@

@@

\bibliographystyle{abbrv}
\bibliography{references}
